One Year HPC Certification Forum in Retrospective

### 2019-04-16 paper.tex
new abstract

\begin{abstract}
  The HPC community has always considered the training of new and existing HPC practitioners to be of high importance to its growth.
  This diversification of HPC practitioners challenges the traditional training approaches, which are not able to satisfy the specific needs of users, often coming from non-traditionally HPC disciplines, and only interested in learning a particular set of competencies.
  Challenges for HPC centres are to identify and overcome the gaps in users’ knowledge, while users struggle to identify relevant skills.

  With the HPC Certification Forum we aim to clearly categorize, define, and examine competencies which brings benefit to all stakeholders involved in training.
  In this article, we report the status and progress this independent body has made during the first year of its existence: processes and prototypes have been drafted that will  mature to a holistic ecosystem beneficial for all stackholders in HPC education.
\end{abstract}

>>>>

\begin{abstract}

The ever-changing nature of HPC has always compelled the HPC community to focus a lot of effort into training of new and existing practitioners. Historically, these efforts were tailored
 around a typical group of users possessing, due to their background, a certain set of programming skills. However, as HPC has become more diverse in terms of hardware, software and 
 the user background, the traditional training approaches became insufficient in addressing training needs of our community. This increasingly complicated HPC landscape makes 
 developement and delivery of new training materials challenging. How should we develop training for users, often coming from non-traditionally HPC disciplines, and only interested in 
 learning a particular set of skills? How can we satisfy their training needs if we don't really understand what these are? It's clear that HPC centres struggle to identify and overcome the 
 gaps in users' knowledge, while users struggle to identify skills required to perform their tasks.

With the HPC Certification Forum we aim to clearly categorise, define, and examine competencies expected from proficient HPC practitioners. 
In this article, we report the status and progress this independent body has made during the first year of its existence. The drafted processes and prototypes are expected to mature into a 
holistic ecosystem beneficial for all stakeholders in HPC education.
\end{abstract}
